---
title: "Analysis_Q3"
author: "Suraj Vidyadaran"
date: "Tuesday, October 27, 2015"
output: word_document
---
#How effective are QVC's on-air broadcast and on-air personalities in driving product sales?

```{r}
#Summarizing the differnt hosts for the On-air broadcast
host_Jan<-as.data.frame(table(product_airtime_Jan$HOST1))
host_Jan<-host_Jan[order(-host_Jan$Freq),]
host_Jan
host_Feb<-as.data.frame(table(product_airtime_Feb$HOST1))
host_Feb<-host_Feb[order(-host_Feb$Freq),]
host_Feb
host_Mar<-as.data.frame(table(product_airtime_March$HOST1))
host_Mar<-host_Mar[order(-host_Mar$Freq),]
host_Mar
```

*So we can see a total of 27 hosts for the On-Air broadcast. We have to analyze the impact of the hosts on the sales of products*


##Analyzing the impact of various TV hosts on the product sales one by one

###Host 1- Brown Jayne
```{r}
library(ggplot2)
library(grid)
library(gridExtra)
Product_airtime_Jan_host1<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Brown Jayne")
Product_airtime_Feb_host1<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Brown Jayne")
Product_airtime_Mar_host1<-subset(product_airtime_March,product_airtime_March$HOST1=="Brown Jayne")

host1_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host1$PRODUCT_DESCRIPTION))
colnames(host1_Jan_pd_tb)<-c("Product","Airtime_no")
host1_Jan_pd_tb<-host1_Jan_pd_tb[order(-host1_Jan_pd_tb$Airtime_no),]
host1_Jan_pd_tb<-host1_Jan_pd_tb[host1_Jan_pd_tb$Airtime_no>0,]
host1_Jan_results<-merge(host1_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host1_Jan_results<-host1_Jan_results[order(-host1_Jan_results$Airtime_no),]
head(host1_Jan_results)
p1<-ggplot(host1_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Brown Jayne in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host1_Jan<-cor(host1_Jan_results$Airtime_no,host1_Jan_results$Jan_orders)
cor_host1_Jan

host1_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host1$PRODUCT_DESCRIPTION))
colnames(host1_Feb_pd_tb)<-c("Product","Airtime_no")
host1_Feb_pd_tb<-host1_Feb_pd_tb[order(-host1_Feb_pd_tb$Airtime_no),]
host1_Feb_pd_tb<-host1_Feb_pd_tb[host1_Feb_pd_tb$Airtime_no>0,]
host1_Feb_results<-merge(host1_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host1_Feb_results<-host1_Feb_results[order(-host1_Feb_results$Airtime_no),]
head(host1_Feb_results)
p2<-ggplot(host1_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Brown Jayne in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host1_Feb<-cor(host1_Feb_results$Airtime_no,host1_Feb_results$Feb_orders)
cor_host1_Feb


host1_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host1$PRODUCT_DESCRIPTION))
colnames(host1_Mar_pd_tb)<-c("Product","Airtime_no")
host1_Mar_pd_tb<-host1_Mar_pd_tb[order(-host1_Mar_pd_tb$Airtime_no),]
host1_Mar_pd_tb<-host1_Mar_pd_tb[host1_Mar_pd_tb$Airtime_no>0,]
host1_Mar_results<-merge(host1_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host1_Mar_results<-host1_Mar_results[order(-host1_Mar_results$Airtime_no),]
head(host1_Mar_results)
p3<-ggplot(host1_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Brown Jayne in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host1_Mar<-cor(host1_Mar_results$Airtime_no,host1_Mar_results$Mar_orders)
cor_host1_Mar

print(p1)
print(p2)
print(p3)
```

###Host 2-Stauffer Stacey

```{r}
library(ggplot2)
library(grid)
library(gridExtra)
Product_airtime_Jan_host2<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Stauffer Stacey")
Product_airtime_Feb_host2<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Stauffer Stacey")
Product_airtime_Mar_host2<-subset(product_airtime_March,product_airtime_March$HOST1=="Stauffer Stacey")

host2_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host2$PRODUCT_DESCRIPTION))
colnames(host2_Jan_pd_tb)<-c("Product","Airtime_no")
host2_Jan_pd_tb<-host2_Jan_pd_tb[order(-host2_Jan_pd_tb$Airtime_no),]
host2_Jan_pd_tb<-host2_Jan_pd_tb[host2_Jan_pd_tb$Airtime_no>0,]
host2_Jan_results<-merge(host2_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host2_Jan_results<-host2_Jan_results[order(-host2_Jan_results$Airtime_no),]
head(host2_Jan_results)
 p1<-ggplot(host2_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Stauffer Stacey in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host2_Jan<-cor(host2_Jan_results$Airtime_no,host2_Jan_results$Jan_orders)
cor_host2_Jan

host2_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host2$PRODUCT_DESCRIPTION))
colnames(host2_Feb_pd_tb)<-c("Product","Airtime_no")
host2_Feb_pd_tb<-host2_Feb_pd_tb[order(-host2_Feb_pd_tb$Airtime_no),]
host2_Feb_pd_tb<-host2_Feb_pd_tb[host2_Feb_pd_tb$Airtime_no>0,]
host2_Feb_results<-merge(host2_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host2_Feb_results<-host2_Feb_results[order(-host2_Feb_results$Airtime_no),]
head(host2_Feb_results)
p2<-ggplot(host2_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Stauffer Stacey in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host2_Feb<-cor(host2_Feb_results$Airtime_no,host2_Feb_results$Feb_orders)
cor_host2_Feb

host2_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host2$PRODUCT_DESCRIPTION))
colnames(host2_Mar_pd_tb)<-c("Product","Airtime_no")
host2_Mar_pd_tb<-host2_Mar_pd_tb[order(-host2_Mar_pd_tb$Airtime_no),]
host2_Mar_pd_tb<-host2_Mar_pd_tb[host2_Mar_pd_tb$Airtime_no>0,]
host2_Mar_results<-merge(host2_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host2_Mar_results<-host2_Mar_results[order(-host2_Mar_results$Airtime_no),]
head(host2_Mar_results)
p3<-ggplot(host2_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Stauffer Stacey in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host2_Mar<-cor(host2_Mar_results$Airtime_no,host2_Mar_results$Mar_orders)
cor_host2_Mar

print(p1)
print(p2)
print(p3)
```

###3)Host 3-Rudolph TreacyJane
```{r}
Product_airtime_Jan_host3<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Rudolph TreacyJane")
Product_airtime_Feb_host3<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Rudolph TreacyJane")
Product_airtime_Mar_host3<-subset(product_airtime_March,product_airtime_March$HOST1=="Rudolph TreacyJane")

host3_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host3$PRODUCT_DESCRIPTION))
colnames(host3_Jan_pd_tb)<-c("Product","Airtime_no")
host3_Jan_pd_tb<-host3_Jan_pd_tb[order(-host3_Jan_pd_tb$Airtime_no),]
host3_Jan_pd_tb<-host3_Jan_pd_tb[order(-host3_Jan_pd_tb$Airtime_no),]
host3_Jan_pd_tb<-host3_Jan_pd_tb[host3_Jan_pd_tb$Airtime_no>0,]
host3_Jan_results<-merge(host3_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host3_Jan_results<-host3_Jan_results[order(-host3_Jan_results$Airtime_no),]
head(host3_Jan_results)
p1<-ggplot(host3_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Rudolph TreacyJane in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host3_Jan<-cor(host3_Jan_results$Airtime_no,host3_Jan_results$Jan_orders)
cor_host3_Jan

host3_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host3$PRODUCT_DESCRIPTION))
colnames(host3_Feb_pd_tb)<-c("Product","Airtime_no")
host3_Feb_pd_tb<-host3_Feb_pd_tb[order(-host3_Feb_pd_tb$Airtime_no),]
host3_Feb_pd_tb<-host3_Feb_pd_tb[host3_Feb_pd_tb$Airtime_no>0,]
host3_Feb_results<-merge(host3_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host3_Feb_results<-host3_Feb_results[order(-host3_Feb_results$Airtime_no),]
head(host3_Feb_results)
p2<-ggplot(host3_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Rudolph TreacyJane in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host3_Feb<-cor(host3_Feb_results$Airtime_no,host3_Feb_results$Feb_orders)
cor_host3_Feb

host3_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host3$PRODUCT_DESCRIPTION))
colnames(host3_Mar_pd_tb)<-c("Product","Airtime_no")
host3_Mar_pd_tb<-host3_Mar_pd_tb[order(-host3_Mar_pd_tb$Airtime_no),]
host3_Mar_pd_tb<-host3_Mar_pd_tb[host3_Mar_pd_tb$Airtime_no>0,]
host3_Mar_results<-merge(host3_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host3_Mar_results<-host3_Mar_results[order(-host3_Mar_results$Airtime_no),]
head(host3_Mar_results)
p3<-ggplot(host3_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Rudolph TreacyJane in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host3_Mar<-cor(host3_Mar_results$Airtime_no,host3_Mar_results$Mar_orders)
cor_host3_Mar

print(p1)
print(p2)
print(p3)
```

###4)Host 4- Hornback Nancy
```{r}
Product_airtime_Jan_host4<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Hornback Nancy")
Product_airtime_Feb_host4<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Hornback Nancy")
Product_airtime_Mar_host4<-subset(product_airtime_March,product_airtime_March$HOST1=="Hornback Nancy")


host4_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host4$PRODUCT_DESCRIPTION))
colnames(host4_Jan_pd_tb)<-c("Product","Airtime_no")
host4_Jan_pd_tb<-host4_Jan_pd_tb[order(-host4_Jan_pd_tb$Airtime_no),]
host4_Jan_pd_tb<-host4_Jan_pd_tb[order(-host4_Jan_pd_tb$Airtime_no),]
host4_Jan_pd_tb<-host4_Jan_pd_tb[host4_Jan_pd_tb$Airtime_no>0,]
host4_Jan_results<-merge(host4_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host4_Jan_results<-host4_Jan_results[order(-host4_Jan_results$Airtime_no),]
head(host4_Jan_results)
p1<-ggplot(host4_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Hornback Nancy in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host4_Jan<-cor(host4_Jan_results$Airtime_no,host4_Jan_results$Jan_orders)
cor_host4_Jan

host4_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host4$PRODUCT_DESCRIPTION))
colnames(host4_Feb_pd_tb)<-c("Product","Airtime_no")
host4_Feb_pd_tb<-host4_Feb_pd_tb[order(-host4_Feb_pd_tb$Airtime_no),]
host4_Feb_pd_tb<-host4_Feb_pd_tb[host4_Feb_pd_tb$Airtime_no>0,]
host4_Feb_results<-merge(host4_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host4_Feb_results<-host4_Feb_results[order(-host4_Feb_results$Airtime_no),]
head(host4_Feb_results)
p2<-ggplot(host4_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Hornback Nancy in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host4_Feb<-cor(host4_Feb_results$Airtime_no,host4_Feb_results$Feb_orders)
cor_host4_Feb

host4_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host4$PRODUCT_DESCRIPTION))
colnames(host4_Mar_pd_tb)<-c("Product","Airtime_no")
host4_Mar_pd_tb<-host4_Mar_pd_tb[order(-host4_Mar_pd_tb$Airtime_no),]
host4_Mar_pd_tb<-host4_Mar_pd_tb[host4_Mar_pd_tb$Airtime_no>0,]
host4_Mar_results<-merge(host4_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host4_Mar_results<-host4_Mar_results[order(-host4_Mar_results$Airtime_no),]
head(host4_Mar_results)
p3<-ggplot(host4_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Hornback Nancy in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host4_Mar<-cor(host4_Mar_results$Airtime_no,host4_Mar_results$Mar_orders)
cor_host4_Mar

print(p1)
print(p2)
print(p3)
```

###5)Host 5- Popaj Alberti
```{r}
Product_airtime_Jan_host5<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Popaj Alberti")
Product_airtime_Feb_host5<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Popaj Alberti")
Product_airtime_Mar_host5<-subset(product_airtime_March,product_airtime_March$HOST1=="Popaj Alberti")


host5_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host5$PRODUCT_DESCRIPTION))
colnames(host5_Jan_pd_tb)<-c("Product","Airtime_no")
host5_Jan_pd_tb<-host5_Jan_pd_tb[order(-host5_Jan_pd_tb$Airtime_no),]
host5_Jan_pd_tb<-host5_Jan_pd_tb[host5_Jan_pd_tb$Airtime_no>0,]
host5_Jan_results<-merge(host5_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host5_Jan_results<-host5_Jan_results[order(-host5_Jan_results$Airtime_no),]
head(host5_Jan_results)
p1<-ggplot(host5_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Popaj Alberti in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host5_Jan<-cor(host5_Jan_results$Airtime_no,host5_Jan_results$Jan_orders)
cor_host5_Jan

host5_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host5$PRODUCT_DESCRIPTION))
colnames(host5_Feb_pd_tb)<-c("Product","Airtime_no")
host5_Feb_pd_tb<-host5_Feb_pd_tb[order(-host5_Feb_pd_tb$Airtime_no),]
host5_Feb_pd_tb<-host5_Feb_pd_tb[host5_Feb_pd_tb$Airtime_no>0,]
host5_Feb_results<-merge(host5_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host5_Feb_results<-host5_Feb_results[order(-host5_Feb_results$Airtime_no),]
head(host5_Feb_results)
p2<-ggplot(host5_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Popaj Alberti in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host5_Feb<-cor(host5_Feb_results$Airtime_no,host5_Feb_results$Feb_orders)
cor_host5_Feb

host5_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host5$PRODUCT_DESCRIPTION))
colnames(host5_Mar_pd_tb)<-c("Product","Airtime_no")
host5_Mar_pd_tb<-host5_Mar_pd_tb[order(-host5_Mar_pd_tb$Airtime_no),]
host5_Mar_pd_tb<-host5_Mar_pd_tb[host5_Mar_pd_tb$Airtime_no>0,]
host5_Mar_results<-merge(host5_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host5_Mar_results<-host5_Mar_results[order(-host5_Mar_results$Airtime_no),]
head(host5_Mar_results)
p3<-ggplot(host5_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Popaj Alberti in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host5_Mar<-cor(host5_Mar_results$Airtime_no,host5_Mar_results$Mar_orders)
cor_host5_Mar

print(p1)
print(p2)
print(p3)
```

###5)Host 5- Popaj Alberti
```{r}
Product_airtime_Jan_host5<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Popaj Alberti")
Product_airtime_Feb_host5<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Popaj Alberti")
Product_airtime_Mar_host5<-subset(product_airtime_March,product_airtime_March$HOST1=="Popaj Alberti")


host5_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host5$PRODUCT_DESCRIPTION))
colnames(host5_Jan_pd_tb)<-c("Product","Airtime_no")
host5_Jan_pd_tb<-host5_Jan_pd_tb[order(-host5_Jan_pd_tb$Airtime_no),]
host5_Jan_pd_tb<-host5_Jan_pd_tb[host5_Jan_pd_tb$Airtime_no>0,]
host5_Jan_results<-merge(host5_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host5_Jan_results<-host5_Jan_results[order(-host5_Jan_results$Airtime_no),]
head(host5_Jan_results)
p1<-ggplot(host5_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Popaj Alberti in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host5_Jan<-cor(host5_Jan_results$Airtime_no,host5_Jan_results$Jan_orders)
cor_host5_Jan

host5_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host5$PRODUCT_DESCRIPTION))
colnames(host5_Feb_pd_tb)<-c("Product","Airtime_no")
host5_Feb_pd_tb<-host5_Feb_pd_tb[order(-host5_Feb_pd_tb$Airtime_no),]
host5_Feb_pd_tb<-host5_Feb_pd_tb[host5_Feb_pd_tb$Airtime_no>0,]
host5_Feb_results<-merge(host5_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host5_Feb_results<-host5_Feb_results[order(-host5_Feb_results$Airtime_no),]
head(host5_Feb_results)
p2<-ggplot(host5_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Popaj Alberti in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host5_Feb<-cor(host5_Feb_results$Airtime_no,host5_Feb_results$Feb_orders)
cor_host5_Feb

host5_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host5$PRODUCT_DESCRIPTION))
colnames(host5_Mar_pd_tb)<-c("Product","Airtime_no")
host5_Mar_pd_tb<-host5_Mar_pd_tb[order(-host5_Mar_pd_tb$Airtime_no),]
host5_Mar_pd_tb<-host5_Mar_pd_tb[host5_Mar_pd_tb$Airtime_no>0,]
host5_Mar_results<-merge(host5_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host5_Mar_results<-host5_Mar_results[order(-host5_Mar_results$Airtime_no),]
head(host5_Mar_results)
p3<-ggplot(host5_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Popaj Alberti in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host5_Mar<-cor(host5_Mar_results$Airtime_no,host5_Mar_results$Mar_orders)
cor_host5_Mar

print(p1)
print(p2)
print(p3)
```

###6)Host 6- Nester Antonella
```{r}
Product_airtime_Jan_host6<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Nester Antonella")
Product_airtime_Feb_host6<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Nester Antonella")
Product_airtime_Mar_host6<-subset(product_airtime_March,product_airtime_March$HOST1=="Nester Antonella")


host6_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host6$PRODUCT_DESCRIPTION))
colnames(host6_Jan_pd_tb)<-c("Product","Airtime_no")
host6_Jan_pd_tb<-host6_Jan_pd_tb[order(-host6_Jan_pd_tb$Airtime_no),]
host6_Jan_pd_tb<-host6_Jan_pd_tb[host6_Jan_pd_tb$Airtime_no>0,]
host6_Jan_results<-merge(host6_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host6_Jan_results<-host6_Jan_results[order(-host6_Jan_results$Airtime_no),]
head(host6_Jan_results)
p1<-ggplot(host6_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Nester Antonella in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host6_Jan<-cor(host6_Jan_results$Airtime_no,host6_Jan_results$Jan_orders)
cor_host6_Jan

host6_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host6$PRODUCT_DESCRIPTION))
colnames(host6_Feb_pd_tb)<-c("Product","Airtime_no")
host6_Feb_pd_tb<-host6_Feb_pd_tb[order(-host6_Feb_pd_tb$Airtime_no),]
host6_Feb_pd_tb<-host6_Feb_pd_tb[host6_Feb_pd_tb$Airtime_no>0,]
host6_Feb_results<-merge(host6_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host6_Feb_results<-host6_Feb_results[order(-host6_Feb_results$Airtime_no),]
head(host6_Feb_results)
p2<-ggplot(host6_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Nester Antonella in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host6_Feb<-cor(host6_Feb_results$Airtime_no,host6_Feb_results$Feb_orders)
cor_host6_Feb

host6_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host6$PRODUCT_DESCRIPTION))
colnames(host6_Mar_pd_tb)<-c("Product","Airtime_no")
host6_Mar_pd_tb<-host6_Mar_pd_tb[order(-host6_Mar_pd_tb$Airtime_no),]
host6_Mar_pd_tb<-host6_Mar_pd_tb[host6_Mar_pd_tb$Airtime_no>0,]
host6_Mar_results<-merge(host6_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host6_Mar_results<-host6_Mar_results[order(-host6_Mar_results$Airtime_no),]
head(host6_Mar_results)
p3<-ggplot(host6_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Nester Antonella in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host6_Mar<-cor(host6_Mar_results$Airtime_no,host6_Mar_results$Mar_orders)
cor_host6_Mar

print(p1)
print(p2)
print(p3)
```

###7)Host 7- Williams Leah
```{r}
Product_airtime_Jan_host7<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Williams Leah")
Product_airtime_Feb_host7<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Williams Leah")
Product_airtime_Mar_host7<-subset(product_airtime_March,product_airtime_March$HOST1=="Williams Leah")


host7_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host7$PRODUCT_DESCRIPTION))
colnames(host7_Jan_pd_tb)<-c("Product","Airtime_no")
host7_Jan_pd_tb<-host7_Jan_pd_tb[order(-host7_Jan_pd_tb$Airtime_no),]
host7_Jan_pd_tb<-host7_Jan_pd_tb[host7_Jan_pd_tb$Airtime_no>0,]
host7_Jan_results<-merge(host7_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host7_Jan_results<-host7_Jan_results[order(-host7_Jan_results$Airtime_no),]
head(host7_Jan_results)
p1<-ggplot(host7_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Williams Leah in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host7_Jan<-cor(host7_Jan_results$Airtime_no,host7_Jan_results$Jan_orders)
cor_host7_Jan

host7_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host7$PRODUCT_DESCRIPTION))
colnames(host7_Feb_pd_tb)<-c("Product","Airtime_no")
host7_Feb_pd_tb<-host7_Feb_pd_tb[order(-host7_Feb_pd_tb$Airtime_no),]
host7_Feb_pd_tb<-host7_Feb_pd_tb[host7_Feb_pd_tb$Airtime_no>0,]
host7_Feb_results<-merge(host7_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host7_Feb_results<-host7_Feb_results[order(-host7_Feb_results$Airtime_no),]
head(host7_Feb_results)
p2<-ggplot(host7_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Williams Leah in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host7_Feb<-cor(host7_Feb_results$Airtime_no,host7_Feb_results$Feb_orders)
cor_host7_Feb

host7_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host7$PRODUCT_DESCRIPTION))
colnames(host7_Mar_pd_tb)<-c("Product","Airtime_no")
host7_Mar_pd_tb<-host7_Mar_pd_tb[order(-host7_Mar_pd_tb$Airtime_no),]
host7_Mar_pd_tb<-host7_Mar_pd_tb[host7_Mar_pd_tb$Airtime_no>0,]
host7_Mar_results<-merge(host7_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host7_Mar_results<-host7_Mar_results[order(-host7_Mar_results$Airtime_no),]
head(host7_Mar_results)
p3<-ggplot(host7_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Williams Leah in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host7_Mar<-cor(host7_Mar_results$Airtime_no,host7_Mar_results$Mar_orders)
cor_host7_Mar

print(p1)
print(p2)
print(p3)
```

###8)Host 8- RoeMary Beth

```{r}
Product_airtime_Jan_host8<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="RoeMary Beth")
Product_airtime_Feb_host8<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="RoeMary Beth")
Product_airtime_Mar_host8<-subset(product_airtime_March,product_airtime_March$HOST1=="RoeMary Beth")


host8_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host8$PRODUCT_DESCRIPTION))
colnames(host8_Jan_pd_tb)<-c("Product","Airtime_no")
host8_Jan_pd_tb<-host8_Jan_pd_tb[order(-host8_Jan_pd_tb$Airtime_no),]
host8_Jan_pd_tb<-host8_Jan_pd_tb[host8_Jan_pd_tb$Airtime_no>0,]
host8_Jan_results<-merge(host8_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host8_Jan_results<-host8_Jan_results[order(-host8_Jan_results$Airtime_no),]
head(host8_Jan_results)
p1<-ggplot(host8_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host RoeMary Beth in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host8_Jan<-cor(host8_Jan_results$Airtime_no,host8_Jan_results$Jan_orders)
cor_host8_Jan

host8_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host8$PRODUCT_DESCRIPTION))
colnames(host8_Feb_pd_tb)<-c("Product","Airtime_no")
host8_Feb_pd_tb<-host8_Feb_pd_tb[order(-host8_Feb_pd_tb$Airtime_no),]
host8_Feb_pd_tb<-host8_Feb_pd_tb[host8_Feb_pd_tb$Airtime_no>0,]
host8_Feb_results<-merge(host8_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host8_Feb_results<-host8_Feb_results[order(-host8_Feb_results$Airtime_no),]
head(host8_Feb_results)
p2<-ggplot(host8_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host RoeMary Beth in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host8_Feb<-cor(host8_Feb_results$Airtime_no,host8_Feb_results$Feb_orders)
cor_host8_Feb

host8_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host8$PRODUCT_DESCRIPTION))
colnames(host8_Mar_pd_tb)<-c("Product","Airtime_no")
host8_Mar_pd_tb<-host8_Mar_pd_tb[order(-host8_Mar_pd_tb$Airtime_no),]
host8_Mar_pd_tb<-host8_Mar_pd_tb[host8_Mar_pd_tb$Airtime_no>0,]
host8_Mar_results<-merge(host8_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host8_Mar_results<-host8_Mar_results[order(-host8_Mar_results$Airtime_no),]
head(host8_Mar_results)
p3<-ggplot(host8_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host RoeMary Beth in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host8_Mar<-cor(host8_Mar_results$Airtime_no,host8_Mar_results$Mar_orders)
cor_host8_Mar

print(p1)
print(p2)
print(p3)
```

###9)Host 9- Hughes Dan

```{r}
Product_airtime_Jan_host9<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Hughes Dan")
Product_airtime_Feb_host9<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Hughes Dan")
Product_airtime_Mar_host9<-subset(product_airtime_March,product_airtime_March$HOST1=="Hughes Dan")


host9_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host9$PRODUCT_DESCRIPTION))
colnames(host9_Jan_pd_tb)<-c("Product","Airtime_no")
host9_Jan_pd_tb<-host9_Jan_pd_tb[order(-host9_Jan_pd_tb$Airtime_no),]
host9_Jan_pd_tb<-host9_Jan_pd_tb[host9_Jan_pd_tb$Airtime_no>0,]
host9_Jan_results<-merge(host9_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host9_Jan_results<-host9_Jan_results[order(-host9_Jan_results$Airtime_no),]
head(host9_Jan_results)
p1<-ggplot(host9_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Hughes Dan in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host9_Jan<-cor(host9_Jan_results$Airtime_no,host9_Jan_results$Jan_orders)
cor_host9_Jan

host9_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host9$PRODUCT_DESCRIPTION))
colnames(host9_Feb_pd_tb)<-c("Product","Airtime_no")
host9_Feb_pd_tb<-host9_Feb_pd_tb[order(-host9_Feb_pd_tb$Airtime_no),]
host9_Feb_pd_tb<-host9_Feb_pd_tb[host9_Feb_pd_tb$Airtime_no>0,]
host9_Feb_results<-merge(host9_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host9_Feb_results<-host9_Feb_results[order(-host9_Feb_results$Airtime_no),]
head(host9_Feb_results)
p2<-ggplot(host9_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Hughes Dan in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host9_Feb<-cor(host9_Feb_results$Airtime_no,host9_Feb_results$Feb_orders)
cor_host9_Feb

host9_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host9$PRODUCT_DESCRIPTION))
colnames(host9_Mar_pd_tb)<-c("Product","Airtime_no")
host9_Mar_pd_tb<-host9_Mar_pd_tb[order(-host9_Mar_pd_tb$Airtime_no),]
host9_Mar_pd_tb<-host9_Mar_pd_tb[host9_Mar_pd_tb$Airtime_no>0,]
host9_Mar_results<-merge(host9_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host9_Mar_results<-host9_Mar_results[order(-host9_Mar_results$Airtime_no),]
head(host9_Mar_results)
p3<-ggplot(host9_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Hughes Dan in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host9_Mar<-cor(host9_Mar_results$Airtime_no,host9_Mar_results$Mar_orders)
cor_host9_Mar

print(p1)
print(p2)
print(p3)
```


###10)Host 10- Killinger Shawn

```{r}
Product_airtime_Jan_host10<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Killinger Shawn")
Product_airtime_Feb_host10<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Killinger Shawn")
Product_airtime_Mar_host10<-subset(product_airtime_March,product_airtime_March$HOST1=="Killinger Shawn")


host10_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host10$PRODUCT_DESCRIPTION))
colnames(host10_Jan_pd_tb)<-c("Product","Airtime_no")
host10_Jan_pd_tb<-host10_Jan_pd_tb[order(-host10_Jan_pd_tb$Airtime_no),]
host10_Jan_pd_tb<-host10_Jan_pd_tb[host10_Jan_pd_tb$Airtime_no>0,]
host10_Jan_results<-merge(host10_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host10_Jan_results<-host10_Jan_results[order(-host10_Jan_results$Airtime_no),]
head(host10_Jan_results)
p1<-ggplot(host10_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Killinger Shawn in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host10_Jan<-cor(host10_Jan_results$Airtime_no,host10_Jan_results$Jan_orders)
cor_host10_Jan

host10_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host10$PRODUCT_DESCRIPTION))
colnames(host10_Feb_pd_tb)<-c("Product","Airtime_no")
host10_Feb_pd_tb<-host10_Feb_pd_tb[order(-host10_Feb_pd_tb$Airtime_no),]
host10_Feb_pd_tb<-host10_Feb_pd_tb[host10_Feb_pd_tb$Airtime_no>0,]
host10_Feb_results<-merge(host10_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host10_Feb_results<-host10_Feb_results[order(-host10_Feb_results$Airtime_no),]
head(host10_Feb_results)
p2<-ggplot(host10_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Killinger Shawn in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host10_Feb<-cor(host10_Feb_results$Airtime_no,host10_Feb_results$Feb_orders)
cor_host10_Feb

host10_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host10$PRODUCT_DESCRIPTION))
colnames(host10_Mar_pd_tb)<-c("Product","Airtime_no")
host10_Mar_pd_tb<-host10_Mar_pd_tb[order(-host10_Mar_pd_tb$Airtime_no),]
host10_Mar_pd_tb<-host10_Mar_pd_tb[host10_Mar_pd_tb$Airtime_no>0,]
host10_Mar_results<-merge(host10_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host10_Mar_results<-host10_Mar_results[order(-host10_Mar_results$Airtime_no),]
head(host10_Mar_results)
p3<-ggplot(host10_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Killinger Shawn in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host10_Mar<-cor(host10_Mar_results$Airtime_no,host10_Mar_results$Mar_orders)
cor_host10_Mar

print(p1)
print(p2)
print(p3)
```

###11)Host 11- James-Dementri Pat

```{r}
Product_airtime_Jan_host11<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="James-Dementri Pat")
Product_airtime_Feb_host11<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="James-Dementri Pat")
Product_airtime_Mar_host11<-subset(product_airtime_March,product_airtime_March$HOST1=="James-Dementri Pat")


host11_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host11$PRODUCT_DESCRIPTION))
colnames(host11_Jan_pd_tb)<-c("Product","Airtime_no")
host11_Jan_pd_tb<-host11_Jan_pd_tb[order(-host11_Jan_pd_tb$Airtime_no),]
host11_Jan_pd_tb<-host11_Jan_pd_tb[host11_Jan_pd_tb$Airtime_no>0,]
host11_Jan_results<-merge(host11_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host11_Jan_results<-host11_Jan_results[order(-host11_Jan_results$Airtime_no),]
head(host11_Jan_results)
p1<-ggplot(host11_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host James-Dementri Pat in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host11_Jan<-cor(host11_Jan_results$Airtime_no,host11_Jan_results$Jan_orders)
cor_host11_Jan

host11_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host11$PRODUCT_DESCRIPTION))
colnames(host11_Feb_pd_tb)<-c("Product","Airtime_no")
host11_Feb_pd_tb<-host11_Feb_pd_tb[order(-host11_Feb_pd_tb$Airtime_no),]
host11_Feb_pd_tb<-host11_Feb_pd_tb[host11_Feb_pd_tb$Airtime_no>0,]
host11_Feb_results<-merge(host11_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host11_Feb_results<-host11_Feb_results[order(-host11_Feb_results$Airtime_no),]
head(host11_Feb_results)
p2<-ggplot(host11_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host James-Dementri Pat in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host11_Feb<-cor(host11_Feb_results$Airtime_no,host11_Feb_results$Feb_orders)
cor_host11_Feb

host11_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host11$PRODUCT_DESCRIPTION))
colnames(host11_Mar_pd_tb)<-c("Product","Airtime_no")
host11_Mar_pd_tb<-host11_Mar_pd_tb[order(-host11_Mar_pd_tb$Airtime_no),]
host11_Mar_pd_tb<-host11_Mar_pd_tb[host11_Mar_pd_tb$Airtime_no>0,]
host11_Mar_results<-merge(host11_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host11_Mar_results<-host11_Mar_results[order(-host11_Mar_results$Airtime_no),]
head(host11_Mar_results)
p3<-ggplot(host11_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host James-Dementri Pat in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host11_Mar<-cor(host11_Mar_results$Airtime_no,host11_Mar_results$Mar_orders)
cor_host11_Mar


print(p1)
print(p2)
print(p3)
```

###12)Host 12- Stran Amy

```{r}
Product_airtime_Jan_host12<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Stran Amy")
Product_airtime_Feb_host12<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Stran Amy")
Product_airtime_Mar_host12<-subset(product_airtime_March,product_airtime_March$HOST1=="Stran Amy")


host12_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host12$PRODUCT_DESCRIPTION))
colnames(host12_Jan_pd_tb)<-c("Product","Airtime_no")
host12_Jan_pd_tb<-host12_Jan_pd_tb[order(-host12_Jan_pd_tb$Airtime_no),]
host12_Jan_pd_tb<-host12_Jan_pd_tb[host12_Jan_pd_tb$Airtime_no>0,]
host12_Jan_results<-merge(host12_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host12_Jan_results<-host12_Jan_results[order(-host12_Jan_results$Airtime_no),]
head(host12_Jan_results)
p1<-ggplot(host12_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Stran Amy in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host12_Jan<-cor(host12_Jan_results$Airtime_no,host12_Jan_results$Jan_orders)
cor_host12_Jan

host12_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host12$PRODUCT_DESCRIPTION))
colnames(host12_Feb_pd_tb)<-c("Product","Airtime_no")
host12_Feb_pd_tb<-host12_Feb_pd_tb[order(-host12_Feb_pd_tb$Airtime_no),]
host12_Feb_pd_tb<-host12_Feb_pd_tb[host12_Feb_pd_tb$Airtime_no>0,]
host12_Feb_results<-merge(host12_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host12_Feb_results<-host12_Feb_results[order(-host12_Feb_results$Airtime_no),]
head(host12_Feb_results)
p2<-ggplot(host12_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Stran Amy in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host12_Feb<-cor(host12_Feb_results$Airtime_no,host12_Feb_results$Feb_orders)
cor_host12_Feb

host12_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host12$PRODUCT_DESCRIPTION))
colnames(host12_Mar_pd_tb)<-c("Product","Airtime_no")
host12_Mar_pd_tb<-host12_Mar_pd_tb[order(-host12_Mar_pd_tb$Airtime_no),]
host12_Mar_pd_tb<-host12_Mar_pd_tb[host12_Mar_pd_tb$Airtime_no>0,]
host12_Mar_results<-merge(host12_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host12_Mar_results<-host12_Mar_results[order(-host12_Mar_results$Airtime_no),]
head(host12_Mar_results)
p3<-ggplot(host12_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Stran Amy in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host12_Mar<-cor(host12_Mar_results$Airtime_no,host12_Mar_results$Mar_orders)
cor_host12_Mar


print(p1)
print(p2)
print(p3)
```

###13)Host 13- Bauer Jill

```{r}
Product_airtime_Jan_host13<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Bauer Jill")
Product_airtime_Feb_host13<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Bauer Jill")
Product_airtime_Mar_host13<-subset(product_airtime_March,product_airtime_March$HOST1=="Bauer Jill")


host13_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host13$PRODUCT_DESCRIPTION))
colnames(host13_Jan_pd_tb)<-c("Product","Airtime_no")
host13_Jan_pd_tb<-host13_Jan_pd_tb[order(-host13_Jan_pd_tb$Airtime_no),]
host13_Jan_pd_tb<-host13_Jan_pd_tb[host13_Jan_pd_tb$Airtime_no>0,]
host13_Jan_results<-merge(host13_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host13_Jan_results<-host13_Jan_results[order(-host13_Jan_results$Airtime_no),]
head(host13_Jan_results)
p1<-ggplot(host13_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Bauer Jill in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host13_Jan<-cor(host13_Jan_results$Airtime_no,host13_Jan_results$Jan_orders)
cor_host13_Jan

host13_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host13$PRODUCT_DESCRIPTION))
colnames(host13_Feb_pd_tb)<-c("Product","Airtime_no")
host13_Feb_pd_tb<-host13_Feb_pd_tb[order(-host13_Feb_pd_tb$Airtime_no),]
host13_Feb_pd_tb<-host13_Feb_pd_tb[host13_Feb_pd_tb$Airtime_no>0,]
host13_Feb_results<-merge(host13_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host13_Feb_results<-host13_Feb_results[order(-host13_Feb_results$Airtime_no),]
head(host13_Feb_results)
p2<-ggplot(host13_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Bauer Jill in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host13_Feb<-cor(host13_Feb_results$Airtime_no,host13_Feb_results$Feb_orders)
cor_host13_Feb

host13_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host13$PRODUCT_DESCRIPTION))
colnames(host13_Mar_pd_tb)<-c("Product","Airtime_no")
host13_Mar_pd_tb<-host13_Mar_pd_tb[order(-host13_Mar_pd_tb$Airtime_no),]
host13_Mar_pd_tb<-host13_Mar_pd_tb[host13_Mar_pd_tb$Airtime_no>0,]
host13_Mar_results<-merge(host13_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host13_Mar_results<-host13_Mar_results[order(-host13_Mar_results$Airtime_no),]
head(host13_Mar_results)
p3<-ggplot(host13_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Bauer Jill in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host13_Mar<-cor(host13_Mar_results$Airtime_no,host13_Mar_results$Mar_orders)
cor_host13_Mar


print(p1)
print(p2)
print(p3)
```

###14)Host 14- Domeier Rick

```{r}
Product_airtime_Jan_host14<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Domeier Rick")
Product_airtime_Feb_host14<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Domeier Rick")
Product_airtime_Mar_host14<-subset(product_airtime_March,product_airtime_March$HOST1=="Domeier Rick")


host14_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host14$PRODUCT_DESCRIPTION))
colnames(host14_Jan_pd_tb)<-c("Product","Airtime_no")
host14_Jan_pd_tb<-host14_Jan_pd_tb[order(-host14_Jan_pd_tb$Airtime_no),]
host14_Jan_pd_tb<-host14_Jan_pd_tb[host14_Jan_pd_tb$Airtime_no>0,]
host14_Jan_results<-merge(host14_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host14_Jan_results<-host14_Jan_results[order(-host14_Jan_results$Airtime_no),]
head(host14_Jan_results)
p1<-ggplot(host14_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Domeier Rick in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host14_Jan<-cor(host14_Jan_results$Airtime_no,host14_Jan_results$Jan_orders)
cor_host14_Jan

host14_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host14$PRODUCT_DESCRIPTION))
colnames(host14_Feb_pd_tb)<-c("Product","Airtime_no")
host14_Feb_pd_tb<-host14_Feb_pd_tb[order(-host14_Feb_pd_tb$Airtime_no),]
host14_Feb_pd_tb<-host14_Feb_pd_tb[host14_Feb_pd_tb$Airtime_no>0,]
host14_Feb_results<-merge(host14_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host14_Feb_results<-host14_Feb_results[order(-host14_Feb_results$Airtime_no),]
head(host14_Feb_results)
p2<-ggplot(host14_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Domeier Rick in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host14_Feb<-cor(host14_Feb_results$Airtime_no,host14_Feb_results$Feb_orders)
cor_host14_Feb

host14_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host14$PRODUCT_DESCRIPTION))
colnames(host14_Mar_pd_tb)<-c("Product","Airtime_no")
host14_Mar_pd_tb<-host14_Mar_pd_tb[order(-host14_Mar_pd_tb$Airtime_no),]
host14_Mar_pd_tb<-host14_Mar_pd_tb[host14_Mar_pd_tb$Airtime_no>0,]
host14_Mar_results<-merge(host14_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host14_Mar_results<-host14_Mar_results[order(-host14_Mar_results$Airtime_no),]
head(host14_Mar_results)
p3<-ggplot(host14_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Domeier Rick in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host14_Mar<-cor(host14_Mar_results$Airtime_no,host14_Mar_results$Mar_orders)
cor_host14_Mar


print(p1)
print(p2)
print(p3)
```

###15)Host 15- Gonzales Jacque

```{r}
Product_airtime_Jan_host15<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Gonzales Jacque")
Product_airtime_Feb_host15<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Gonzales Jacque")
Product_airtime_Mar_host15<-subset(product_airtime_March,product_airtime_March$HOST1=="Gonzales Jacque")


host15_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host15$PRODUCT_DESCRIPTION))
colnames(host15_Jan_pd_tb)<-c("Product","Airtime_no")
host15_Jan_pd_tb<-host15_Jan_pd_tb[order(-host15_Jan_pd_tb$Airtime_no),]
host15_Jan_pd_tb<-host15_Jan_pd_tb[host15_Jan_pd_tb$Airtime_no>0,]
host15_Jan_results<-merge(host15_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host15_Jan_results<-host15_Jan_results[order(-host15_Jan_results$Airtime_no),]
head(host15_Jan_results)
p1<-ggplot(host15_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Gonzales Jacque in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host15_Jan<-cor(host15_Jan_results$Airtime_no,host15_Jan_results$Jan_orders)
cor_host15_Jan

host15_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host15$PRODUCT_DESCRIPTION))
colnames(host15_Feb_pd_tb)<-c("Product","Airtime_no")
host15_Feb_pd_tb<-host15_Feb_pd_tb[order(-host15_Feb_pd_tb$Airtime_no),]
host15_Feb_pd_tb<-host15_Feb_pd_tb[host15_Feb_pd_tb$Airtime_no>0,]
host15_Feb_results<-merge(host15_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host15_Feb_results<-host15_Feb_results[order(-host15_Feb_results$Airtime_no),]
head(host15_Feb_results)
p2<-ggplot(host15_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Gonzales Jacque in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host15_Feb<-cor(host15_Feb_results$Airtime_no,host15_Feb_results$Feb_orders)
cor_host15_Feb

host15_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host15$PRODUCT_DESCRIPTION))
colnames(host15_Mar_pd_tb)<-c("Product","Airtime_no")
host15_Mar_pd_tb<-host15_Mar_pd_tb[order(-host15_Mar_pd_tb$Airtime_no),]
host15_Mar_pd_tb<-host15_Mar_pd_tb[host15_Mar_pd_tb$Airtime_no>0,]
host15_Mar_results<-merge(host15_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host15_Mar_results<-host15_Mar_results[order(-host15_Mar_results$Airtime_no),]
head(host15_Mar_results)
p3<-ggplot(host15_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Gonzales Jacque in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host15_Mar<-cor(host15_Mar_results$Airtime_no,host15_Mar_results$Mar_orders)
cor_host15_Mar


print(p1)
print(p2)
print(p3)
```


###16)Host 16- Lindquist Kerstin

```{r}
Product_airtime_Jan_host16<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Lindquist Kerstin")
Product_airtime_Feb_host16<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Lindquist Kerstin")
Product_airtime_Mar_host16<-subset(product_airtime_March,product_airtime_March$HOST1=="Lindquist Kerstin")


host16_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host16$PRODUCT_DESCRIPTION))
colnames(host16_Jan_pd_tb)<-c("Product","Airtime_no")
host16_Jan_pd_tb<-host16_Jan_pd_tb[order(-host16_Jan_pd_tb$Airtime_no),]
host16_Jan_pd_tb<-host16_Jan_pd_tb[host16_Jan_pd_tb$Airtime_no>0,]
host16_Jan_results<-merge(host16_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host16_Jan_results<-host16_Jan_results[order(-host16_Jan_results$Airtime_no),]
head(host16_Jan_results)
p1<-ggplot(host16_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Lindquist Kerstin in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host16_Jan<-cor(host16_Jan_results$Airtime_no,host16_Jan_results$Jan_orders)
cor_host16_Jan

host16_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host16$PRODUCT_DESCRIPTION))
colnames(host16_Feb_pd_tb)<-c("Product","Airtime_no")
host16_Feb_pd_tb<-host16_Feb_pd_tb[order(-host16_Feb_pd_tb$Airtime_no),]
host16_Feb_pd_tb<-host16_Feb_pd_tb[host16_Feb_pd_tb$Airtime_no>0,]
host16_Feb_results<-merge(host16_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host16_Feb_results<-host16_Feb_results[order(-host16_Feb_results$Airtime_no),]
head(host16_Feb_results)
p2<-ggplot(host16_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Lindquist Kerstin in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host16_Feb<-cor(host16_Feb_results$Airtime_no,host16_Feb_results$Feb_orders)
cor_host16_Feb

host16_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host16$PRODUCT_DESCRIPTION))
colnames(host16_Mar_pd_tb)<-c("Product","Airtime_no")
host16_Mar_pd_tb<-host16_Mar_pd_tb[order(-host16_Mar_pd_tb$Airtime_no),]
host16_Mar_pd_tb<-host16_Mar_pd_tb[host16_Mar_pd_tb$Airtime_no>0,]
host16_Mar_results<-merge(host16_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host16_Mar_results<-host16_Mar_results[order(-host16_Mar_results$Airtime_no),]
head(host16_Mar_results)
p3<-ggplot(host16_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Lindquist Kerstin in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host16_Mar<-cor(host16_Mar_results$Airtime_no,host16_Mar_results$Mar_orders)
cor_host16_Mar


print(p1)
print(p2)
print(p3)
```


###17)Host 17- Coffey Jennifer

```{r}
Product_airtime_Jan_host17<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Coffey Jennifer")
Product_airtime_Feb_host17<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Coffey Jennifer")
Product_airtime_Mar_host17<-subset(product_airtime_March,product_airtime_March$HOST1=="Coffey Jennifer")


host17_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host17$PRODUCT_DESCRIPTION))
colnames(host17_Jan_pd_tb)<-c("Product","Airtime_no")
host17_Jan_pd_tb<-host17_Jan_pd_tb[order(-host17_Jan_pd_tb$Airtime_no),]
host17_Jan_pd_tb<-host17_Jan_pd_tb[host17_Jan_pd_tb$Airtime_no>0,]
host17_Jan_results<-merge(host17_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host17_Jan_results<-host17_Jan_results[order(-host17_Jan_results$Airtime_no),]
head(host17_Jan_results)
p1<-ggplot(host17_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Coffey Jennifer in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host17_Jan<-cor(host17_Jan_results$Airtime_no,host17_Jan_results$Jan_orders)
cor_host17_Jan

host17_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host17$PRODUCT_DESCRIPTION))
colnames(host17_Feb_pd_tb)<-c("Product","Airtime_no")
host17_Feb_pd_tb<-host17_Feb_pd_tb[order(-host17_Feb_pd_tb$Airtime_no),]
host17_Feb_pd_tb<-host17_Feb_pd_tb[host17_Feb_pd_tb$Airtime_no>0,]
host17_Feb_results<-merge(host17_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host17_Feb_results<-host17_Feb_results[order(-host17_Feb_results$Airtime_no),]
head(host17_Feb_results)
p2<-ggplot(host17_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Coffey Jennifer in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host17_Feb<-cor(host17_Feb_results$Airtime_no,host17_Feb_results$Feb_orders)
cor_host17_Feb

host17_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host17$PRODUCT_DESCRIPTION))
colnames(host17_Mar_pd_tb)<-c("Product","Airtime_no")
host17_Mar_pd_tb<-host17_Mar_pd_tb[order(-host17_Mar_pd_tb$Airtime_no),]
host17_Mar_pd_tb<-host17_Mar_pd_tb[host17_Mar_pd_tb$Airtime_no>0,]
host17_Mar_results<-merge(host17_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host17_Mar_results<-host17_Mar_results[order(-host17_Mar_results$Airtime_no),]
head(host17_Mar_results)
p3<-ggplot(host17_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Coffey Jennifer in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host17_Mar<-cor(host17_Mar_results$Airtime_no,host17_Mar_results$Mar_orders)
cor_host17_Mar


print(p1)
print(p2)
print(p3)
```


###18)Host 18- Irvin Albany

```{r}
Product_airtime_Jan_host18<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Irvin Albany")
Product_airtime_Feb_host18<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Irvin Albany")
Product_airtime_Mar_host18<-subset(product_airtime_March,product_airtime_March$HOST1=="Irvin Albany")


host18_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host18$PRODUCT_DESCRIPTION))
colnames(host18_Jan_pd_tb)<-c("Product","Airtime_no")
host18_Jan_pd_tb<-host18_Jan_pd_tb[order(-host18_Jan_pd_tb$Airtime_no),]
host18_Jan_pd_tb<-host18_Jan_pd_tb[host18_Jan_pd_tb$Airtime_no>0,]
host18_Jan_results<-merge(host18_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host18_Jan_results<-host18_Jan_results[order(-host18_Jan_results$Airtime_no),]
head(host18_Jan_results)
p1<-ggplot(host18_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Irvin Albany in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host18_Jan<-cor(host18_Jan_results$Airtime_no,host18_Jan_results$Jan_orders)
cor_host18_Jan

host18_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host18$PRODUCT_DESCRIPTION))
colnames(host18_Feb_pd_tb)<-c("Product","Airtime_no")
host18_Feb_pd_tb<-host18_Feb_pd_tb[order(-host18_Feb_pd_tb$Airtime_no),]
host18_Feb_pd_tb<-host18_Feb_pd_tb[host18_Feb_pd_tb$Airtime_no>0,]
host18_Feb_results<-merge(host18_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host18_Feb_results<-host18_Feb_results[order(-host18_Feb_results$Airtime_no),]
head(host18_Feb_results)
p2<-ggplot(host18_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Irvin Albany in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host18_Feb<-cor(host18_Feb_results$Airtime_no,host18_Feb_results$Feb_orders)
cor_host18_Feb

host18_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host18$PRODUCT_DESCRIPTION))
colnames(host18_Mar_pd_tb)<-c("Product","Airtime_no")
host18_Mar_pd_tb<-host18_Mar_pd_tb[order(-host18_Mar_pd_tb$Airtime_no),]
host18_Mar_pd_tb<-host18_Mar_pd_tb[host18_Mar_pd_tb$Airtime_no>0,]
host18_Mar_results<-merge(host18_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host18_Mar_results<-host18_Mar_results[order(-host18_Mar_results$Airtime_no),]
head(host18_Mar_results)
p3<-ggplot(host18_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Irvin Albany in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host18_Mar<-cor(host18_Mar_results$Airtime_no,host18_Mar_results$Mar_orders)
cor_host18_Mar


print(p1)
print(p2)
print(p3)
```


###19)Host 19- Bennett Sandra

```{r}
Product_airtime_Jan_host19<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Bennett Sandra")
Product_airtime_Feb_host19<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Bennett Sandra")
Product_airtime_Mar_host19<-subset(product_airtime_March,product_airtime_March$HOST1=="Bennett Sandra")


host19_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host19$PRODUCT_DESCRIPTION))
colnames(host19_Jan_pd_tb)<-c("Product","Airtime_no")
host19_Jan_pd_tb<-host19_Jan_pd_tb[order(-host19_Jan_pd_tb$Airtime_no),]
host19_Jan_pd_tb<-host19_Jan_pd_tb[host19_Jan_pd_tb$Airtime_no>0,]
host19_Jan_results<-merge(host19_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host19_Jan_results<-host19_Jan_results[order(-host19_Jan_results$Airtime_no),]
head(host19_Jan_results)
p1<-ggplot(host19_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Bennett Sandra in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host19_Jan<-cor(host19_Jan_results$Airtime_no,host19_Jan_results$Jan_orders)
cor_host19_Jan

host19_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host19$PRODUCT_DESCRIPTION))
colnames(host19_Feb_pd_tb)<-c("Product","Airtime_no")
host19_Feb_pd_tb<-host19_Feb_pd_tb[order(-host19_Feb_pd_tb$Airtime_no),]
host19_Feb_pd_tb<-host19_Feb_pd_tb[host19_Feb_pd_tb$Airtime_no>0,]
host19_Feb_results<-merge(host19_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host19_Feb_results<-host19_Feb_results[order(-host19_Feb_results$Airtime_no),]
head(host19_Feb_results)
p2<-ggplot(host19_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Bennett Sandra in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host19_Feb<-cor(host19_Feb_results$Airtime_no,host19_Feb_results$Feb_orders)
cor_host19_Feb

host19_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host19$PRODUCT_DESCRIPTION))
colnames(host19_Mar_pd_tb)<-c("Product","Airtime_no")
host19_Mar_pd_tb<-host19_Mar_pd_tb[order(-host19_Mar_pd_tb$Airtime_no),]
host19_Mar_pd_tb<-host19_Mar_pd_tb[host19_Mar_pd_tb$Airtime_no>0,]
host19_Mar_results<-merge(host19_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host19_Mar_results<-host19_Mar_results[order(-host19_Mar_results$Airtime_no),]
head(host19_Mar_results)
p3<-ggplot(host19_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Bennett Sandra in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host19_Mar<-cor(host19_Mar_results$Airtime_no,host19_Mar_results$Mar_orders)
cor_host19_Mar


print(p1)
print(p2)
print(p3)
```

###20)Host 20- Gracie Carolyn

```{r}
Product_airtime_Jan_host20<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Gracie Carolyn")
Product_airtime_Feb_host20<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Gracie Carolyn")
Product_airtime_Mar_host20<-subset(product_airtime_March,product_airtime_March$HOST1=="Gracie Carolyn")


host20_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host20$PRODUCT_DESCRIPTION))
colnames(host20_Jan_pd_tb)<-c("Product","Airtime_no")
host20_Jan_pd_tb<-host20_Jan_pd_tb[order(-host20_Jan_pd_tb$Airtime_no),]
host20_Jan_pd_tb<-host20_Jan_pd_tb[host20_Jan_pd_tb$Airtime_no>0,]
host20_Jan_results<-merge(host20_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host20_Jan_results<-host20_Jan_results[order(-host20_Jan_results$Airtime_no),]
head(host20_Jan_results)
p1<-ggplot(host20_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Gracie Carolyn in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host20_Jan<-cor(host20_Jan_results$Airtime_no,host20_Jan_results$Jan_orders)
cor_host20_Jan

host20_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host20$PRODUCT_DESCRIPTION))
colnames(host20_Feb_pd_tb)<-c("Product","Airtime_no")
host20_Feb_pd_tb<-host20_Feb_pd_tb[order(-host20_Feb_pd_tb$Airtime_no),]
host20_Feb_pd_tb<-host20_Feb_pd_tb[host20_Feb_pd_tb$Airtime_no>0,]
host20_Feb_results<-merge(host20_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host20_Feb_results<-host20_Feb_results[order(-host20_Feb_results$Airtime_no),]
head(host20_Feb_results)
p2<-ggplot(host20_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Gracie Carolyn in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host20_Feb<-cor(host20_Feb_results$Airtime_no,host20_Feb_results$Feb_orders)
cor_host20_Feb

host20_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host20$PRODUCT_DESCRIPTION))
colnames(host20_Mar_pd_tb)<-c("Product","Airtime_no")
host20_Mar_pd_tb<-host20_Mar_pd_tb[order(-host20_Mar_pd_tb$Airtime_no),]
host20_Mar_pd_tb<-host20_Mar_pd_tb[host20_Mar_pd_tb$Airtime_no>0,]
host20_Mar_results<-merge(host20_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host20_Mar_results<-host20_Mar_results[order(-host20_Mar_results$Airtime_no),]
head(host20_Mar_results)
p3<-ggplot(host20_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Gracie Carolyn in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host20_Mar<-cor(host20_Mar_results$Airtime_no,host20_Mar_results$Mar_orders)
cor_host20_Mar


print(p1)
print(p2)
print(p3)
```

###21)Host 21- Boesing Rachel

```{r}
Product_airtime_Jan_host21<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Boesing Rachel")
Product_airtime_Feb_host21<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Boesing Rachel")
Product_airtime_Mar_host21<-subset(product_airtime_March,product_airtime_March$HOST1=="Boesing Rachel")


host21_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host21$PRODUCT_DESCRIPTION))
colnames(host21_Jan_pd_tb)<-c("Product","Airtime_no")
host21_Jan_pd_tb<-host21_Jan_pd_tb[order(-host21_Jan_pd_tb$Airtime_no),]
host21_Jan_pd_tb<-host21_Jan_pd_tb[host21_Jan_pd_tb$Airtime_no>0,]
host21_Jan_results<-merge(host21_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host21_Jan_results<-host21_Jan_results[order(-host21_Jan_results$Airtime_no),]
head(host21_Jan_results)
p1<-ggplot(host21_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Boesing Rachel in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host21_Jan<-cor(host21_Jan_results$Airtime_no,host21_Jan_results$Jan_orders)
cor_host21_Jan

host21_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host21$PRODUCT_DESCRIPTION))
colnames(host21_Feb_pd_tb)<-c("Product","Airtime_no")
host21_Feb_pd_tb<-host21_Feb_pd_tb[order(-host21_Feb_pd_tb$Airtime_no),]
host21_Feb_pd_tb<-host21_Feb_pd_tb[host21_Feb_pd_tb$Airtime_no>0,]
host21_Feb_results<-merge(host21_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host21_Feb_results<-host21_Feb_results[order(-host21_Feb_results$Airtime_no),]
head(host21_Feb_results)
p2<-ggplot(host21_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Boesing Rachel in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host21_Feb<-cor(host21_Feb_results$Airtime_no,host21_Feb_results$Feb_orders)
cor_host21_Feb

host21_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host21$PRODUCT_DESCRIPTION))
colnames(host21_Mar_pd_tb)<-c("Product","Airtime_no")
host21_Mar_pd_tb<-host21_Mar_pd_tb[order(-host21_Mar_pd_tb$Airtime_no),]
host21_Mar_pd_tb<-host21_Mar_pd_tb[host21_Mar_pd_tb$Airtime_no>0,]
host21_Mar_results<-merge(host21_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host21_Mar_results<-host21_Mar_results[order(-host21_Mar_results$Airtime_no),]
head(host21_Mar_results)
p3<-ggplot(host21_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Boesing Rachel in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host21_Mar<-cor(host21_Mar_results$Airtime_no,host21_Mar_results$Mar_orders)
cor_host21_Mar


print(p1)
print(p2)
print(p3)
```


###22)Host 22- Venable David

```{r}
Product_airtime_Jan_host22<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Venable David")
Product_airtime_Feb_host22<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Venable David")
Product_airtime_Mar_host22<-subset(product_airtime_March,product_airtime_March$HOST1=="Venable David")


host22_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host22$PRODUCT_DESCRIPTION))
colnames(host22_Jan_pd_tb)<-c("Product","Airtime_no")
host22_Jan_pd_tb<-host22_Jan_pd_tb[order(-host22_Jan_pd_tb$Airtime_no),]
host22_Jan_pd_tb<-host22_Jan_pd_tb[host22_Jan_pd_tb$Airtime_no>0,]
host22_Jan_results<-merge(host22_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host22_Jan_results<-host22_Jan_results[order(-host22_Jan_results$Airtime_no),]
head(host22_Jan_results)
p1<-ggplot(host22_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Venable David in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host22_Jan<-cor(host22_Jan_results$Airtime_no,host22_Jan_results$Jan_orders)
cor_host22_Jan

host22_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host22$PRODUCT_DESCRIPTION))
colnames(host22_Feb_pd_tb)<-c("Product","Airtime_no")
host22_Feb_pd_tb<-host22_Feb_pd_tb[order(-host22_Feb_pd_tb$Airtime_no),]
host22_Feb_pd_tb<-host22_Feb_pd_tb[host22_Feb_pd_tb$Airtime_no>0,]
host22_Feb_results<-merge(host22_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host22_Feb_results<-host22_Feb_results[order(-host22_Feb_results$Airtime_no),]
head(host22_Feb_results)
p2<-ggplot(host22_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Venable David in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host22_Feb<-cor(host22_Feb_results$Airtime_no,host22_Feb_results$Feb_orders)
cor_host22_Feb

host22_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host22$PRODUCT_DESCRIPTION))
colnames(host22_Mar_pd_tb)<-c("Product","Airtime_no")
host22_Mar_pd_tb<-host22_Mar_pd_tb[order(-host22_Mar_pd_tb$Airtime_no),]
host22_Mar_pd_tb<-host22_Mar_pd_tb[host22_Mar_pd_tb$Airtime_no>0,]
host22_Mar_results<-merge(host22_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host22_Mar_results<-host22_Mar_results[order(-host22_Mar_results$Airtime_no),]
head(host22_Mar_results)
p3<-ggplot(host22_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Venable David in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host22_Mar<-cor(host22_Mar_results$Airtime_no,host22_Mar_results$Mar_orders)
cor_host22_Mar


print(p1)
print(p2)
print(p3)
```

###23)Host 23- Abiera Gabrielle

```{r}
Product_airtime_Jan_host23<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Abiera Gabrielle")
Product_airtime_Feb_host23<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Abiera Gabrielle")
Product_airtime_Mar_host23<-subset(product_airtime_March,product_airtime_March$HOST1=="Abiera Gabrielle")


host23_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host23$PRODUCT_DESCRIPTION))
colnames(host23_Jan_pd_tb)<-c("Product","Airtime_no")
host23_Jan_pd_tb<-host23_Jan_pd_tb[order(-host23_Jan_pd_tb$Airtime_no),]
host23_Jan_pd_tb<-host23_Jan_pd_tb[host23_Jan_pd_tb$Airtime_no>0,]
host23_Jan_results<-merge(host23_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host23_Jan_results<-host23_Jan_results[order(-host23_Jan_results$Airtime_no),]
head(host23_Jan_results)
p1<-ggplot(host23_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Abiera Gabrielle in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host23_Jan<-cor(host23_Jan_results$Airtime_no,host23_Jan_results$Jan_orders)
cor_host23_Jan

host23_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host23$PRODUCT_DESCRIPTION))
colnames(host23_Feb_pd_tb)<-c("Product","Airtime_no")
host23_Feb_pd_tb<-host23_Feb_pd_tb[order(-host23_Feb_pd_tb$Airtime_no),]
host23_Feb_pd_tb<-host23_Feb_pd_tb[host23_Feb_pd_tb$Airtime_no>0,]
host23_Feb_results<-merge(host23_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host23_Feb_results<-host23_Feb_results[order(-host23_Feb_results$Airtime_no),]
head(host23_Feb_results)
p2<-ggplot(host23_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Abiera Gabrielle in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host23_Feb<-cor(host23_Feb_results$Airtime_no,host23_Feb_results$Feb_orders)
cor_host23_Feb

host23_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host23$PRODUCT_DESCRIPTION))
colnames(host23_Mar_pd_tb)<-c("Product","Airtime_no")
host23_Mar_pd_tb<-host23_Mar_pd_tb[order(-host23_Mar_pd_tb$Airtime_no),]
host23_Mar_pd_tb<-host23_Mar_pd_tb[host23_Mar_pd_tb$Airtime_no>0,]
host23_Mar_results<-merge(host23_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host23_Mar_results<-host23_Mar_results[order(-host23_Mar_results$Airtime_no),]
head(host23_Mar_results)
p3<-ggplot(host23_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Abiera Gabrielle in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host23_Mar<-cor(host23_Mar_results$Airtime_no,host23_Mar_results$Mar_orders)
cor_host23_Mar


print(p1)
print(p2)
print(p3)
```

###24)Host 24- Faetsch Sharon

```{r}
Product_airtime_Jan_host24<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Faetsch Sharon")
Product_airtime_Feb_host24<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Faetsch Sharon")
Product_airtime_Mar_host24<-subset(product_airtime_March,product_airtime_March$HOST1=="Faetsch Sharon")


host24_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host24$PRODUCT_DESCRIPTION))
colnames(host24_Jan_pd_tb)<-c("Product","Airtime_no")
host24_Jan_pd_tb<-host24_Jan_pd_tb[order(-host24_Jan_pd_tb$Airtime_no),]
host24_Jan_pd_tb<-host24_Jan_pd_tb[host24_Jan_pd_tb$Airtime_no>0,]
host24_Jan_results<-merge(host24_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host24_Jan_results<-host24_Jan_results[order(-host24_Jan_results$Airtime_no),]
head(host24_Jan_results)
p1<-ggplot(host24_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Faetsch Sharon in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host24_Jan<-cor(host24_Jan_results$Airtime_no,host24_Jan_results$Jan_orders)
cor_host24_Jan

host24_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host24$PRODUCT_DESCRIPTION))
colnames(host24_Feb_pd_tb)<-c("Product","Airtime_no")
host24_Feb_pd_tb<-host24_Feb_pd_tb[order(-host24_Feb_pd_tb$Airtime_no),]
host24_Feb_pd_tb<-host24_Feb_pd_tb[host24_Feb_pd_tb$Airtime_no>0,]
host24_Feb_results<-merge(host24_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host24_Feb_results<-host24_Feb_results[order(-host24_Feb_results$Airtime_no),]
head(host24_Feb_results)
p2<-ggplot(host24_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Faetsch Sharon in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host24_Feb<-cor(host24_Feb_results$Airtime_no,host24_Feb_results$Feb_orders)
cor_host24_Feb

host24_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host24$PRODUCT_DESCRIPTION))
colnames(host24_Mar_pd_tb)<-c("Product","Airtime_no")
host24_Mar_pd_tb<-host24_Mar_pd_tb[order(-host24_Mar_pd_tb$Airtime_no),]
host24_Mar_pd_tb<-host24_Mar_pd_tb[host24_Mar_pd_tb$Airtime_no>0,]
host24_Mar_results<-merge(host24_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host24_Mar_results<-host24_Mar_results[order(-host24_Mar_results$Airtime_no),]
head(host24_Mar_results)
p3<-ggplot(host24_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Faetsch Sharon in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host24_Mar<-cor(host24_Mar_results$Airtime_no,host24_Mar_results$Mar_orders)
cor_host24_Mar


print(p1)
print(p2)
print(p3)
```


###25)Host 25- Cason Courtney

```{r}
Product_airtime_Jan_host25<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Cason Courtney")
Product_airtime_Feb_host25<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Cason Courtney")
Product_airtime_Mar_host25<-subset(product_airtime_March,product_airtime_March$HOST1=="Cason Courtney")


host25_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host25$PRODUCT_DESCRIPTION))
colnames(host25_Jan_pd_tb)<-c("Product","Airtime_no")
host25_Jan_pd_tb<-host25_Jan_pd_tb[order(-host25_Jan_pd_tb$Airtime_no),]
host25_Jan_pd_tb<-host25_Jan_pd_tb[host25_Jan_pd_tb$Airtime_no>0,]
host25_Jan_results<-merge(host25_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host25_Jan_results<-host25_Jan_results[order(-host25_Jan_results$Airtime_no),]
head(host25_Jan_results)
p1<-ggplot(host25_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Cason Courtney in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host25_Jan<-cor(host25_Jan_results$Airtime_no,host25_Jan_results$Jan_orders)
cor_host25_Jan

host25_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host25$PRODUCT_DESCRIPTION))
colnames(host25_Feb_pd_tb)<-c("Product","Airtime_no")
host25_Feb_pd_tb<-host25_Feb_pd_tb[order(-host25_Feb_pd_tb$Airtime_no),]
host25_Feb_pd_tb<-host25_Feb_pd_tb[host25_Feb_pd_tb$Airtime_no>0,]
host25_Feb_results<-merge(host25_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host25_Feb_results<-host25_Feb_results[order(-host25_Feb_results$Airtime_no),]
head(host25_Feb_results)
p2<-ggplot(host25_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Cason Courtney in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host25_Feb<-cor(host25_Feb_results$Airtime_no,host25_Feb_results$Feb_orders)
cor_host25_Feb

host25_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host25$PRODUCT_DESCRIPTION))
colnames(host25_Mar_pd_tb)<-c("Product","Airtime_no")
host25_Mar_pd_tb<-host25_Mar_pd_tb[order(-host25_Mar_pd_tb$Airtime_no),]
host25_Mar_pd_tb<-host25_Mar_pd_tb[host25_Mar_pd_tb$Airtime_no>0,]
host25_Mar_results<-merge(host25_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host25_Mar_results<-host25_Mar_results[order(-host25_Mar_results$Airtime_no),]
head(host25_Mar_results)
p3<-ggplot(host25_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Cason Courtney in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host25_Mar<-cor(host25_Mar_results$Airtime_no,host25_Mar_results$Mar_orders)
cor_host25_Mar


print(p1)
print(p2)
print(p3)
```

###26)Host 26- Wheeler Dan

```{r}
Product_airtime_Jan_host26<-subset(product_airtime_Jan,product_airtime_Jan$HOST1=="Wheeler Dan")
Product_airtime_Feb_host26<-subset(product_airtime_Feb,product_airtime_Feb$HOST1=="Wheeler Dan")
Product_airtime_Mar_host26<-subset(product_airtime_March,product_airtime_March$HOST1=="Wheeler Dan")


host26_Jan_pd_tb<-as.data.frame(table(Product_airtime_Jan_host26$PRODUCT_DESCRIPTION))
colnames(host26_Jan_pd_tb)<-c("Product","Airtime_no")
host26_Jan_pd_tb<-host26_Jan_pd_tb[order(-host26_Jan_pd_tb$Airtime_no),]
host26_Jan_pd_tb<-host26_Jan_pd_tb[host26_Jan_pd_tb$Airtime_no>0,]
host26_Jan_results<-merge(host26_Jan_pd_tb,Jan_Order_Prod_desc,by="Product")
host26_Jan_results<-host26_Jan_results[order(-host26_Jan_results$Airtime_no),]
head(host26_Jan_results)
p1<-ggplot(host26_Jan_results,aes(x=Airtime_no,y=Jan_orders))+geom_point(size=5)+geom_smooth(method="lm",se=TRUE)+xlab("Total air time by host Wheeler Dan in January")+ylab("Total product sales in January")+ggtitle("Correlation between Host airtime and Product Sales in January")
cor_host26_Jan<-cor(host26_Jan_results$Airtime_no,host26_Jan_results$Jan_orders)
cor_host26_Jan

host26_Feb_pd_tb<-as.data.frame(table(Product_airtime_Feb_host26$PRODUCT_DESCRIPTION))
colnames(host26_Feb_pd_tb)<-c("Product","Airtime_no")
host26_Feb_pd_tb<-host26_Feb_pd_tb[order(-host26_Feb_pd_tb$Airtime_no),]
host26_Feb_pd_tb<-host26_Feb_pd_tb[host26_Feb_pd_tb$Airtime_no>0,]
host26_Feb_results<-merge(host26_Feb_pd_tb,Feb_Order_Prod_desc,by="Product")
host26_Feb_results<-host26_Feb_results[order(-host26_Feb_results$Airtime_no),]
head(host26_Feb_results)
p2<-ggplot(host26_Feb_results,aes(x=Airtime_no,y=Feb_orders))+geom_point(size=5,color="darkgreen")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Wheeler Dan in February")+ylab("Total product sales in February")+ggtitle("Correlation between Host airtime and Product Sales in February")
cor_host26_Feb<-cor(host26_Feb_results$Airtime_no,host26_Feb_results$Feb_orders)
cor_host26_Feb

host26_Mar_pd_tb<-as.data.frame(table(Product_airtime_Mar_host26$PRODUCT_DESCRIPTION))
colnames(host26_Mar_pd_tb)<-c("Product","Airtime_no")
host26_Mar_pd_tb<-host26_Mar_pd_tb[order(-host26_Mar_pd_tb$Airtime_no),]
host26_Mar_pd_tb<-host26_Mar_pd_tb[host26_Mar_pd_tb$Airtime_no>0,]
host26_Mar_results<-merge(host26_Mar_pd_tb,Mar_Order_Prod_desc,by="Product")
host26_Mar_results<-host26_Mar_results[order(-host26_Mar_results$Airtime_no),]
head(host26_Mar_results)
p3<-ggplot(host26_Mar_results,aes(x=Airtime_no,y=Mar_orders))+geom_point(size=5,color="orange")+geom_smooth(method="lm",se=TRUE,color="black")+xlab("Total air time by host Wheeler Dan in March")+ylab("Total product sales in March")+ggtitle("Correlation between Host airtime and Product Sales in March")
cor_host26_Mar<-cor(host26_Mar_results$Airtime_no,host26_Mar_results$Mar_orders)
cor_host26_Mar


print(p1)
print(p2)
print(p3)
```