---
title: "Temple_Analytics _Challenge"
author: "Suraj Vidyadaran"
date: "Saturday, October 17, 2015"
output: html_document
---

This Data analysis is done as a part of Temple University Analytics challenge to perform data analytics on big data. For more details about the challenge visit<http://ibit.temple.edu/analytics/>

The analysis is done in QVC data to answer the following questions:

####1)What are the products and product categories of QVC which sells best in the US market?
####2)How effective are QVC's campaigns in driving product sales?
####3)How effective are QVC's on-air broadcast and on-air personalities in driving product sales?
####4)What is the impact of QVC's social networking presence on driving product sales?


##Step 1- Read the data

**Read Customer Master Data**

customer_master <- read.csv("F:/Analytics Challenge/full data/customer_master.csv")
```{r}
head(customer_master)
```

**Read the Email Campaign Data set**

email_campaign <- read.csv("F:/Analytics Challenge/full data/email_campaign.csv")

```{r}
head(email_campaign)
```

**Read the Order Master Data set**

order_master <- read.csv("F:/Analytics Challenge/full data/order_master.csv")


**Read the Product airtime data**

product_airtime <- read.csv("F:/Analytics Challenge/full data/product_airtime.csv")
```{r}
head(product_airtime)
```
**Read the Product Master Data**

product_master <- read.csv("F:/Analytics Challenge/full data/product_master.csv")
```{r}
head(product_master)
```
**Read the Social Network Data**

social <- read.csv("F:/Analytics Challenge/full data/social.csv")
```{r}
head(social)
```
##Step 2:Exploratory Data Analysis

**1)Customer Master Data**
```{r}
#Generating the overall summary

summary(customer_master)
```

```{r}
#Sales per  US states

Customer_States<-as.data.frame(table(customer_master$STATE))
colnames(Customer_States)<-c("State","Sales")
Customer_States<-Customer_States[order(-Customer_States$Sales),]
Customer_States
```

#### A mapping visualization to view the distribution of sales per state
```{r,message=FALSE,warning=FALSE}
require(datasets)
states<-as.data.frame(state.abb)
colnames(states)<-c("State")
Customer_States<-merge(states,Customer_States,by="State")


library(googleVis)
States<-gvisGeoChart(Customer_States,"State","Sales",
                     options=list(region="US",
                                  displayMode="regions",
                                  resolution="provinces",
                                  width=600,height=400))
plot(States)


```


```{r}
#Calculate the percentage of sales per state
Sales_state_percentage<-as.data.frame(prop.table(table(customer_master$STATE))*100)
colnames(Sales_state_percentage)<-c("State","Sales_percent")
Sales_state_percentage<-Sales_state_percentage[order(-Sales_state_percentage$Sales_percent),]
Sales_state_percentage


```

```{r}

# Customer proportion in the code segment

table(customer_master$SHOPPER_SEGMENT_CODE)
segemnt_code_prop<-prop.table(table(customer_master$SHOPPER_SEGMENT_CODE))
segemnt_code_prop
plot(customer_master$SHOPPER_SEGMENT_CODE,col="red",main="Customer Segement distribution",xlab="Segment Code",ylab="Frequency")
```

```{r}
#Proportion of yes and no
table(customer_master$EMAIL_HOLD_IND)

# No of new customer emails
table(customer_master$EMAIL_JANUARAY_ONLY_HOLD_IND)

#Subsettiing customers with email sent
customer_email<-subset(customer_master,customer_master$EMAIL_HOLD_IND=="Y")
head(customer_email)

#If the emails are sent NULL shop segemnt code are more
table(customer_email$SHOPPER_SEGMENT_CODE)
```

```{r}
#Proportion of new customers
table(customer_master$NEW_CUSTOMER_IND)
#Plot the new customers
plot(customer_master$NEW_CUSTOMER_IND,col="green",main="New Customers",xlab="New Customer",ylab="Numbers")

#Calculating the percentage of new customers
percentage_new_customers<-(new_customers/(new_customers+old_customers))*100
percentage_new_customers
library(ggplot2)
ggplot(customer_master,aes(x=factor(""),fill=NEW_CUSTOMER_IND))+geom_bar()+coord_polar("y",start=0)+scale_x_discrete("")+scale_fill_brewer(palette = "Dark2")
```

**2)Email Campaign Data**
```{r}
#Checking the basic summary and structure
summary(email_campaign)
str(email_campaign)
```

```{r}

#Changing the format of Date and generating a new attribute month
email_campaign$CAMPAIGN_DATE<-as.Date(email_campaign$CAMPAIGN_DATE,"%m/%d/%Y")
email_campaign$CAMPAIGN_MONTH<-months(email_campaign$CAMPAIGN_DATE)

#Subsetting the data based on the months
email_campaign_January<-subset(email_campaign,email_campaign$CAMPAIGN_MONTH=="January")
head(email_campaign_January)

#Calculating the total money spent on email campaign in January
total_January<-sum(email_campaign_January$CAMPAIGN_SPEND)
total_January

#Checking for which categories  more money spent
table(email_campaign_January$PRODUCT_CATEGORY)

#Analysis of February
email_campaign_February<-subset(email_campaign,email_campaign$CAMPAIGN_MONTH=="February")
head(email_campaign_February)
total_February<-sum(email_campaign_February$CAMPAIGN_SPEND)
total_February
table(email_campaign_February$PRODUCT_CATEGORY)

#Analysis of March
email_campaign_March<-subset(email_campaign,email_campaign$CAMPAIGN_MONTH=="March")
total_March<-sum(email_campaign_March$CAMPAIGN_SPEND)
total_March
head(email_campaign_March)
table(email_campaign_March$PRODUCT_CATEGORY)
```


**3)Product Master Data**

```{r}
#Exploring the structure of product master
str(product_master)
```

**4) Order Master Data**
```{r results='hide',message=FALSE,eval=FALSE}
#Explore the summary and structure
summary(order_master)
str(order_master)

#Changing the order date format and creating a new attribute month
order_master$ORDER_DATE<-as.Date(order_master$ORDER_DATE,"%Y-%m-%d")
str(order_master$ORDER_DATE)
order_master$ORDER_MONTH<-months(order_master$ORDER_DATE)

```


```{r,eval=FALSE}

#Split and subset order master based on Months
order_January<-subset(order_master,order_master$ORDER_MONTH=="January")
order_February<-subset(order_master,order_master$ORDER_MONTH=="February")
order_March<-subset(order_master,order_master$ORDER_MONTH=="March")

rm(order_master)
```

**5)Product Airtime Data**
```{r}
#Analysing the structure and summary
summary(product_airtime)
str(product_airtime)

#Merge product airtime with product master using product number
product_airtime<-merge(product_master,product_airtime,by="PRODUCT_NBR")
head(product_airtime)

#Changing the format of the date,sort it and create a new attribute month
str(product_airtime$ONAIR_DATE)
product_airtime$ONAIR_DATE<-as.Date(product_airtime$ONAIR_DATE,format = "%Y-%m-%d")
str(product_airtime$ONAIR_DATE)
product_airtime<-product_airtime[order(product_airtime$ONAIR_DATE),]
product_airtime$ONAIR_MONTH<-months(product_airtime$ONAIR_DATE)

# Subset product airtime into three groups based on months
product_airtime_Jan<-subset(product_airtime,product_airtime$ONAIR_MONTH=="January")
product_airtime_Feb<-subset(product_airtime,product_airtime$ONAIR_MONTH=="February")
product_airtime_March<-subset(product_airtime,product_airtime$ONAIR_MONTH=="March")
```
